  ---
title: "Fatality Analysis Reporting System (FARS)"
author: "Savinay Sehgal"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Package Description
`Week4BuildingRPackages` package reads and plots Fatality Analysis Reporting System data from the [US National Highway Traffic Safety Administration]

[FARS] is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes

## Load Packages

```{r}
library(Week4BuildingRPackages)
library(maps)
library(tidyr)
library(magrittr)
library(dplyr)
library(readr)
```

## Included data

Data files included within the package are:

```{r}
list.files(system.file("extdata", package = "Week4BuildingRPackages"))
```

## Package Functions

### Function `make_filename`

This function makes a file in CSV format which is related to the given year: 

```{r}
yr <- 2013
make_filename(yr)
```

### Function `fars_read_years`

This function takes an input as years and then filters the information for that given list

```{r}
fars_read_years(2013)
```


### Function `fars_summarize_years`

This function takes an input as years and then summarizes the information for that given list

```{r}
fars_summarize_years(2013)
```

### Function `fars_map_state`

This function takes an input as year and state.num. It then display that information
in graphical format

```{r}
state_num <- 1
yr <- 2013
fars_map_state(state_num, yr)
```
